Summary for the stimuli selection experiment

### 2021-01-28 material/prerating/data/summary.Rmd
organised files and updated readme
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
add new plots with 3 or 2 raters
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Summary for the stimuli selection experiment"
output: html_notebook
---

@@

## Plot
- Error bars represent SEM.
```{r summary_plot, echo = FALSE}
plot <- ggplot(summary_data, aes(x = stimCategory, y = meanRating)) +
  geom_bar(stat = 'identity') +
  geom_errorbar(aes(ymin = meanRating-SEM, ymax = meanRating + SEM), width=.2,
                 position=position_dodge(.9)) +
  facet_wrap(ratingCategory ~ .)
plot
```
**Comments:**

@@

>>>>

---
title: "Summary for the stimuli selection experiment"
output: html_notebook
---
- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

# Descriptive Stats for the generated stimuli

@@

## Plot
- Error bars represent SEM.
```{r summary_plot, echo = FALSE}
plot <- ggplot(summary_data, aes(x = stimCategory, y = meanRating)) +
  geom_bar(stat = 'identity') +
  geom_errorbar(aes(ymin = meanRating-SEM, ymax = meanRating + SEM), width=.2,
                 position=position_dodge(.9)) +
  facet_wrap(ratingCategory ~ .)
plot
```
**Comments**

@@

# Ranking for the generated stimuli
### High performance
- summed the rating for both articulation and dynamics and ranked the performances

### with 3 raters
```{r ranking-high, echo = FALSE}
data_high <- data_high[order(midFile, ratingCategory)]
data_high_sep <- data_high[, .(N = .N, Sum = sum(rating)), by = .(midFile, ratingCategory)]
data_high_both <- data_high[, .(N = .N, Sum = sum(rating)), by = .(midFile)]

data_high_both[order(-Sum)]
```

### with 2 raters
```{r ranking-high-2, echo = FALSE}
data_high_2 <- data_high[subjectNumber != 3]
data_high_sep_2 <- data_high_2[, .(N = .N, Sum = sum(rating)), by = .(midFile, ratingCategory)]
data_high_both_2 <- data_high_2[, .(N = .N, Sum = sum(rating)), by = .(midFile)]

data_high_both_2[order(-Sum)]
```

### Articulation performance
- summed the rating for both articulation and dynamics and ranked the performances

### with 3 raters
```{r ranking-art, echo = FALSE}
data_art <- data_art[order(midFile, ratingCategory)]
data_art_sep <- data_art[, .(N = .N, Sum = sum(rating)), by = .(midFile, ratingCategory)]
data_art_both <- data_art[, .(N = .N, Sum = sum(rating)), by = .(midFile)]

data_art_both[order(-Sum)]
```

### Difference (not sum)
- calculated the difference between the rating for articulation and the rating for dynamics and ranked the performances

```{r ranking-art-diff, echo = FALSE}
# or difference
data_art_diff <- cbind(data_art[ratingCategory == "articulation"], data_art[ratingCategory == "dynamics"])
data_art_diff$Diff <- 0
colnames(data_art_diff)[c(5,11)] <- c("rating1", "rating2")
data_art_diff$Diff <- data_art_diff$rating1 - data_art_diff$rating2
data_art_diff_both <- data_art_diff[, .(N = .N, Diff = sum(Diff)), by = .(midFile)]

data_art_diff_both[order(-Diff)]
```

### with 2 raters
```{r ranking-art-2, echo = FALSE}
data_art_2 <- data_art[subjectNumber != 3]
data_art_sep_2 <- data_art_2[, .(N = .N, Sum = sum(rating)), by = .(midFile, ratingCategory)]
data_art_both_2 <- data_art_2[, .(N = .N, Sum = sum(rating)), by = .(midFile)]

data_art_both_2[order(-Sum)]
```

### Dynamics performance
- summed the rating for both articulation and dynamics and ranked the performances

### with 3 raters
```{r ranking-dyn, echo = FALSE}
data_dyn <- data_dyn[order(midFile, ratingCategory)]
data_dyn_sep <- data_dyn[, .(N = .N, Sum = sum(rating)), by = .(midFile, ratingCategory)]
data_dyn_both <- data_dyn[, .(N = .N, Sum = sum(rating)), by = .(midFile)]

data_dyn_both[order(-Sum)]
```

### Difference (not sum)
- calculated the difference between the rating for articulation and the rating for dynamics and ranked the performances

```{r ranking-dyn-diff, echo = FALSE}
# or difference
data_dyn_diff <- cbind(data_dyn[ratingCategory == "dynamics"], data_dyn[ratingCategory == "articulation"])
data_dyn_diff$Diff <- 0
colnames(data_dyn_diff)[c(5,11)] <- c("rating1", "rating2")
data_dyn_diff$Diff <- data_dyn_diff$rating1 - data_dyn_diff$rating2
data_dyn_diff_both <- data_dyn_diff[, .(N = .N, Diff = sum(Diff)), by = .(midFile)]

data_dyn_diff_both[order(-Diff)]
```

### with 2 raters
```{r ranking-dyn-2, echo = FALSE}
data_dyn_2 <- data_dyn[subjectNumber != 3]
data_dyn_sep_2 <- data_dyn_2[, .(N = .N, Sum = sum(rating)), by = .(midFile, ratingCategory)]
data_dyn_both_2 <- data_dyn_2[, .(N = .N, Sum = sum(rating)), by = .(midFile)]

data_dyn_both_2[order(-Sum)]
```

### Low performance
- summed the rating for both articulation and dynamics and ranked the performances

### with 3 raters
```{r ranking-low, echo = FALSE}
data_low <- data_low[order(midFile, ratingCategory)]
data_low_sep <- data_low[, .(N = .N, Sum = sum(rating)), by = .(midFile, ratingCategory)]
data_low_both <- data_low[, .(N = .N, Sum = sum(rating)), by = .(midFile)]

data_low_both[order(Sum)]
```

### with 2 raters
```{r ranking-low-2, echo = FALSE}
data_low_2 <- data_low[subjectNumber != 3]
data_low_sep_2 <- data_low_2[, .(N = .N, Sum = sum(rating)), by = .(midFile, ratingCategory)]
data_low_both_2 <- data_low_2[, .(N = .N, Sum = sum(rating)), by = .(midFile)]

data_low_both_2[order(Sum)]
```
